The Effects of weather on maize yield: New evidence from Kenya

### 2018-12-26 writing/draft3/draft19.tex
writing..

Adjusted $R^2$ is not available for the linear mixed models. To get an approximation of the adjusted $R^2$, we estimated ordinary least squares (OLS) with the same explanatory variables which were included in our preferred linear mixed models as the fixed effects (see the list of variables in table~\ref{MainEst}). For each of the three samples (all counties, ASAL and non-ASAL) we estimated two variants of the OLS, one with the dummy variables for the counties and one without them. The values of the adjusted $R^2$ are summarasied in table~\ref{R2}.

>>>>

The AIC is an important criterion for comparison of competing models, however it does not provide any information about the absolute goodness of fit. In order to assess the absolute goodness of fit of a model, a different measure is needed. For a simple linear regression, the coeffiecient of determination $R^2$ or its adjusted variant is typically used for this purpose. Nevertheless, obtaining the $R^2$ or the adjusted $R^2$ is not straightforward for linear mixed models or for models estimated by the maximum likelihood in general. In this study, we used the coefficient of determination of generalized linear mixed-effects models introduced by \cite{Nakagawa2013}. For each of our samples (all counties, ASAL and non-ASAL), we present two versions of the statistic in table~\ref{R2}. These include marginal $R^2$ which can be interpreted as the variance explained by the fixed effects components and the conditional $R^2$ which can be interpreted as the variance explained by both fixed effects and random effects. In this case, the only random effects are the intercepts, hence the difference between the two variants is the variance explained by the random intercepts. As is apparent from table~\ref{R2}, the fixed effects explain about $30\%$ of the variance in case of the model for all counties.
